Natural variation in teosinte at the domestication locus teosinte branched1 (tb1)

### 2014-05-11 manuscript.tex
edits
working through TP and TKs text edits; updated refs

In order to assess patterns of linkage disequilibrium (LD) around the Hopscotch element in the context of chromosomal patterns of LD we used Tassel \citep{Bradbury2007} and calculated LD between SNPs across chromosome 1 using previously published data from twelve plants each of the Ejutla A, Ejutla B, San Lorenzo, and La Mesa populations \citep{Pyhajarvi2013}. We chose these populations because we had both genotyping data for the Hopscotch as well as chromosome-wide SNP data for chromosome 1. For each population we filtered the initial set of 5,897 SNPs on chromosome 1 to accept only SNPs with a minor allele frequency of at least 0.1, resulting in 1,671, 3,023, 3,122, and 2,167 SNPs for San Lorenzo, Ejutla B, Ejutla A, and La Mesa, respectively. We then used Tassel \citep{Bradbury2007} to calculate linkage disequilibrium ($r^{2}$) across chromosome 1 for each population.

@@

To investigate the phenotypic effects of the Hopscotch insertion in teosinte, we conducted an initial phenotyping trial (Phenotyping 1). We germinated 250 seeds of \emph{parviglumis} collected in Jalisco state, Mexico (population San Lorenzo) \citep{Hufford2010} where the Hopscotch is segregating at highest frequency (0.44) in our initial genotyping sample set. In order to maximize the likelihood of finding the Hopscotch in our association population we selected seeds from sites where genotyped individuals were homozygous or heterozygous for the insertion. We chose between 10-13 seeds from each of 23 sampling sites. We treated seeds with fungicide and germinated them in petri dishes with filter paper. Successful germinations (206 individuals) were then planted into one gallon size pots with potting soil and randomly spaced one foot apart on greenhouse benches. Plants were watered three times a day with an automatic drip containing 10-20-10 fertilizer. \lev{it ended up being a combination of drip and hand watering because they dried out so much and did better when they had water on the leaves as well as in the soil}

>>>>

In order to assess patterns of linkage disequilibrium (LD) around the Hopscotch element in the context of chromosomal patterns of LD we used Tassel \citep{Bradbury2007} and calculated LD between SNPs across chromosome 1 using previously published data from twelve plants each of the Ejutla A (EjuA), Ejutla B (EjuB), San Lorenzo (SLO), and La Mesa (MSA) populations \citep{Pyhajarvi2013}. We chose these populations because we had both genotyping data for the Hopscotch as well as chromosome-wide SNP data for chromosome 1. For each population we filtered the initial set of 5,897 SNPs on chromosome 1 to accept only SNPs with a minor allele frequency of at least 0.1, resulting in 1,671, 3,023, 3,122, and 2,167 SNPs for SLO, EjuB, EjuA, and MSA, respectively. We then used Tassel \citep{Bradbury2007} to calculate linkage disequilibrium ($r^{2}$) across chromosome 1 for each population.

@@

To investigate the phenotypic effects of the Hopscotch insertion in teosinte, we conducted an initial phenotyping trial (Phenotyping 1). We germinated 250 seeds of \emph{parviglumis} collected in Jalisco state, Mexico (population San Lorenzo) \citep{Hufford2010} where the Hopscotch is segregating at highest frequency (0.44) in our initial genotyping sample set. In order to maximize the likelihood of finding the Hopscotch in our association population we selected seeds from sites where genotyped individuals were homozygous or heterozygous for the insertion. We chose between 10-13 seeds from each of 23 sampling sites. We treated seeds with fungicide and germinated them in petri dishes with filter paper. Following germination, 206 successful germinations were then planted into one gallon size pots with potting soil and randomly spaced one foot apart on greenhouse benches. Plants were watered three times a day with an automatic drip containing 10-20-10 fertilizer. \lev{it ended up being a combination of drip and hand watering because they dried out so much and did better when they had water on the leaves as well as in the soil}
